Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-11-28 Paper.Rmd
replied to edited Data section

The database comprises measurements of soil organic carbon and total soil nitrogen (Mg C or N per m$^{2}$ of soil surface) 

@@

<!--***DAN: Can you check this please? I do not think it can be right. The values on Fig. 3a range from close to 0 to over 3000. 3000 would be 3000 Mg C. I do not think a cubic meter of soil even weighs that much, including all the carbon and non-carbon components.-->

@@

<!--***DAN: Shya, please add a sup mat figure showing the sampling locations and a link to it here in place of the X-->

@@

<!--***DAN: Shya to add units, and replace X and Y with autolinks that give the numbers-->
<!--***Shya: These species number for birds and mammals came from the processed data without any NA and -ve(unrealistic) mass, is that okay? 
for example, species of birds [@Mcnab_2009] raw data (the xls file you gave me) shows 712 species out of which some have NA in both mass and BMR column and one entry has -ve mass!!!-->
<!--***DAN: Yes, that makes sense, but please go back to the data as published, which should be a supporting appendix to the original publications, and make sure I have not given you erroneous data-->

>>>>

The database comprises measurements of soil organic carbon and total soil nitrogen (Mg C or N per hectare of soil surface) 

@@

<!--***DAN: Can you check this please? I do not think it can be right. The values on Fig. 3a range from close to 0 to over 3000. 3000 would be 3000 Mg C. I do not think a cubic meter of soil even weighs that much, including all the carbon and non-carbon components.
***Shya: I checked : it should be megagram per hectare, Wills2014 reference is for stock of Carbon, not for nitrogen, Prof. loecke told me nitrogen data is not published yet. He screened locations which had both soil C and N stocks after omiting NAs.-->

@@

<!--***DAN: Shya, please add a sup mat figure showing the sampling locations and a link to it here in place of the X
***Shya: once Prof. Loecke give me the lattitude and longitudes, I will do that.-->

@@

### 2018-11-28 SupportingInformation.Rmd
reply to editted Data section : still need to discus
replied to edited Data section

```{r read_BMR_birds_and_copulaplot, echo=F, results='hide'}
set.seed(seed)
raw_b<-readxl::read_xls("./Data/BMR/BirdBodyMassesMetabolicRates/BirdMassesAndMetabolicRatesMcNab2008.xls")
raw_b<-raw_b[,1:3]
raw_b<-na.omit(raw_b)
raw_b<-raw_b[,2:3]
raw_b<-as.data.frame(raw_b)
raw_b[303,2]<-0.66  #to convert as numeric
raw_b[,2]<-as.numeric(raw_b[,2])
raw_b<-raw_b[-which(raw_b[,1]<0),]  # omit -ve mass?

@@

>>>>

```{r read_BMR_birds_and_copulaplot, echo=F, results='hide'}
set.seed(seed)
raw_b<-readxl::read_xls("./Data/BMR/BirdBodyMassesMetabolicRates/BirdMassesAndMetabolicRatesMcNab2008.xls")
raw_b<-raw_b[,1:3]
raw_b<-na.omit(raw_b)
raw_b<-raw_b[,2:3]
raw_b<-as.data.frame(raw_b)

saveRDS(raw_b,"./Data/BMR/BirdBodyMassesMetabolicRates/my_birdsBMR_data.RDS")

@@

saveRDS(raw_m,"./Data/BMR/MammalianBodyMassesMetabolicRates/my_mammalsBMR_data.RDS")
